Modeling the Evolution of Mimicry

### 2016-02-24 docs/paper/Paper.tex
Revert "Revert "More formtting""
This reverts commit 2cc5e3dd1f6627b38d8fa264cd300954f0530773.

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/Batesplate_ArM}
	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row). \cite{bates1862}}
	\label{fig:batesian-butterfly}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.5]{../tex/images/Punctuated-equilibrium}
	\caption[Punctuated equilibrium vs. phyletic gradualism]{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism. Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
	\label{fig:punctuated-equilibrium}
\end{figure}

@@

\begin{table}[H]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{1.5cm} | >{\centering} p{1cm} | p{5cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Force Factor & 40 & A unit vector is multiplied by this amount before being added to the force vector.\\ \hline
		Differential Time Step (DT) & 0.01 & The time step used for first-order integration of the motion equations.\\ \hline
		Friction & 5 & The friction constant used for motion calculations.\\ \hline
		Work Factor & 1 & \( Work done = WF * force * distance \), where \(WF\) is this constant.\\
	\hline
\end{tabular}
\caption{Parameters to control mobility of agents.}
\label{tab:mobility-control-parameters}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=5]{../tex/images/CA_rule30s}
	\caption[Cellular Automata]{Cellular Automata Rule 30.
	Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
	\label{fig:cellular-automata-rule-30}
\end{figure}

\begin{table}[H]
	\centering
	\setlength\tabcolsep{2pt}
	\begin{tabular}{| p{2.2cm} | c | c | c | c | c | c | c | c |}
	  \hline
	  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
	  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
	  \hline
	\end{tabular}
	\caption{Cellular Automata rule}
	\label{tab:cellular-automata-rule}
\end{table}

@@

\begin{table}[H]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{|c|c|c|c|}
	\hline
		\textbf{Pattern(8)} & \textbf{Palatability(2)} & \textbf{Mobility(6)} & \textbf{Reproduction(1)} \\ \hline
		10101101					 	& 							01		 		 & 			110001					&					1						 		 \\ \hline
\end{tabular}
\caption{Distribution and purpose of each gene of the 17 bit prey genome.}
\label{tab:prey-genome}
\end{table}

@@

\begin{algorithm}[H]
	\caption{Algorithm for updating position of the Prey species}
	\label{algo:algorithm-movement-prey}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $forceMagnitude \gets convertToDecimal(genome[10-15])$
			\STATE Get list of neighborhood cells, sorted by population of prey species.
			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[H]
	\caption{Algorithm for reproduction of the Predator species}
	\label{algo:algorithm-reproduction-predator}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $capableToReproduce \gets$ true or false depending on the 5th bit of the genome, and maturity on reproduction age.
			\IF {$capableToReproduce == true$ and $currentCellPopulationOfPredators > 1$ } 
				\STATE $anotherPredator \gets$ Select random predator from same cell.
				\IF {$anotherPredator$ is alive and $capableToReproduce$ and also reached reproduction maturity age}
					\STATE Perform genetic cross over and mutation to create new genome.
					\STATE Create new predator with new genome and zero memory, and release into environment.
					\STATE Record reproduction time for both predators.
				\ENDIF
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

\subsection{Initial configuration with two prey species}
\label{subsec:init-conf-2prey}
% Put the table here
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 108 
  														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  & 108 
  					 									& \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 2 prey species}
\label{tab:config-table-2-prey}
\end{table}

@@

% Put the image
\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
	\label{fig:plot-2-prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime5k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
	\label{fig:plot-2-prey-5k}
\end{figure}

@@

%Put the number of rings picture:
\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-2Prey}
	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
	\label{fig:ringSize10k-2Prey}
\end{figure}

@@

%CARule table
\begin{table}[h]
\centering
\begin{tabular}{|l|c|c|c|}
  \hline
  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule60}} 
  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule61}} 
  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule62}}\\
  \hline
\end{tabular}
\caption{Difference in prey pattern genotype and phenotype}
\label{tab:diff-in-pattern}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey-generated-prey}
	\caption[Population distribution of generated mimicry rings (2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
	\label{fig:plot-2-prey-generated-prey}
\end{figure}

@@

\subsection{Initial configuration with four prey species}
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
  																										& 50 & \multicolumn{2}{c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1400} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species}
\label{tab:config-table-4-prey}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-4Prey}
	\caption[Population distribution of mimicry rings (4 prey species)]{Population distribution of mimicry rings, initialized with 4 prey species.}
	\label{fig:plot-4-prey}
\end{figure}

@@

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{Predator configuration} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  	 & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}  & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species with increased population}
\label{tab:config-table-4-more-prey}
\end{table}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10K-4MorePrey}
	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:plot-4-more-prey}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4MorePrey}
	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:ringSize10k-4MorePrey}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/Batesplate_ArM}
	\caption[Plate from Bates (1862) illustrating Batesian mimicry]{Plate from Bates (1862) illustrating Batesian mimicry between Dismorphia species (top row, third row) and various Ithomiini (Nymphalidae) (second row, bottom row). \cite{bates1862}}
	\label{fig:batesian-butterfly}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.5]{../tex/images/Punctuated-equilibrium}
	\caption[Punctuated equilibrium vs. phyletic gradualism]{Punctuated equilibrium, bottom, consists of morphological stability and rare bursts of evolutionary change, while the top explains phyletic gradualism. Image source: \href{http://en.wikipedia.org/wiki/Punctuated_equilibrium}{Wikipedia}}
	\label{fig:punctuated-equilibrium}
\end{figure}

@@

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{1.5cm} | >{\centering} p{1cm} | p{5cm} |}
	\hline
		\textbf{Parameter} & \textbf{Value} & \textbf{Description} \\ \hline
		Force Factor & 40 & A unit vector is multiplied by this amount before being added to the force vector.\\ \hline
		Differential Time Step (DT) & 0.01 & The time step used for first-order integration of the motion equations.\\ \hline
		Friction & 5 & The friction constant used for motion calculations.\\ \hline
		Work Factor & 1 & \( Work done = WF * force * distance \), where \(WF\) is this constant.\\
	\hline
\end{tabular}
\caption{Parameters to control mobility of agents.}
\label{tab:mobility-control-parameters}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=5]{../tex/images/CA_rule30s}
	\caption[Cellular Automata]{Cellular Automata Rule 30.
	Image source: \href{http://en.wikipedia.org/wiki/Cellular_automata}{Wikipedia}}
	\label{fig:cellular-automata-rule-30}
\end{figure}

\begin{table}[h]
	\centering
	\setlength\tabcolsep{2pt}
	\begin{tabular}{| p{2.2cm} | c | c | c | c | c | c | c | c |}
	  \hline
	  Current Pattern & 111 & 110 & 101 & 100 & 011 & 010 & 001 & 000 \\ \hline
	  New state of center cell & 0 & 0 & 0 & 1 & 1 & 1 & 1 & 0 \\
	  \hline
	\end{tabular}
	\caption{Cellular Automata rule}
	\label{tab:cellular-automata-rule}
\end{table}

@@

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{|c|c|c|c|}
	\hline
		\textbf{Pattern(8)} & \textbf{Palatability(2)} & \textbf{Mobility(6)} & \textbf{Reproduction(1)} \\ \hline
		10101101					 	& 							01		 		 & 			110001					&					1						 		 \\ \hline
\end{tabular}
\caption{Distribution and purpose of each gene of the 17 bit prey genome.}
\label{tab:prey-genome}
\end{table}

@@

\begin{algorithm}[h]
	\caption{Algorithm for updating position of the Prey species}
	\label{algo:algorithm-movement-prey}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $forceMagnitude \gets convertToDecimal(genome[10-15])$
			\STATE Get list of neighborhood cells, sorted by population of prey species.
			\STATE From the sorted cell list choose the one with the least number of predators and most number of prey.
			\STATE Move towards the selected cell with $forceMagnitude$ unit of force.
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

\begin{algorithm}[h]
	\caption{Algorithm for reproduction of the Predator species}
	\label{algo:algorithm-reproduction-predator}
	\begin{algorithmic}
		\FOR{each step in time}
			\STATE $capableToReproduce \gets$ true or false depending on the 5th bit of the genome, and maturity on reproduction age.
			\IF {$capableToReproduce == true$ and $currentCellPopulationOfPredators > 1$ } 
				\STATE $anotherPredator \gets$ Select random predator from same cell.
				\IF {$anotherPredator$ is alive and $capableToReproduce$ and also reached reproduction maturity age}
					\STATE Perform genetic cross over and mutation to create new genome.
					\STATE Create new predator with new genome and zero memory, and release into environment.
					\STATE Record reproduction time for both predators.
				\ENDIF
			\ENDIF
		\ENDFOR
	\end{algorithmic}
\end{algorithm}

@@

\subsection{Initial configuration with two prey species}
\label{subsec:init-conf-2prey}
% Put the table here
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
  \multirow{2}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 108 
  														& \multicolumn{2}{c|}{\multirow{2}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  & 108 
  					 									& \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1200} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 2 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 2 prey species}
\label{tab:config-table-2-prey}
\end{table}

@@

% Put the image
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 10k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 10k iterations}
	\label{fig:plot-2-prey}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime5k-2Prey}
	\caption[Population distribution of mimicry rings (2 prey species, 5k iterations)]{Population distribution of mimicry rings, initialized with 2 prey species, 5k iterations.}
	\label{fig:plot-2-prey-5k}
\end{figure}

@@

%Put the number of rings picture:
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-2Prey}
	\caption[Number of mimicry rings (2 prey species)]{Number of mimicry rings, initialized with 2 prey species.}
	\label{fig:ringSize10k-2Prey}
\end{figure}

@@

%CARule table
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{|l|c|c|c|}
  \hline
  CA Rule & \(60 \equiv 00111100\) & \(61 \equiv 00111101\) & \(62 \equiv 00111110 \) \\ \hline
  Pattern & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule60}} 
  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule61}} 
  				& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule62}}\\
  \hline
\end{tabular}
\caption{Difference in prey pattern genotype and phenotype}
\label{tab:diff-in-pattern}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-2Prey-generated-prey}
	\caption[Population distribution of generated mimicry rings (2 prey species)]{Population distribution of generated mimicry rings, initialized with 2 prey species.}
	\label{fig:plot-2-prey-generated-prey}
\end{figure}

@@

\subsection{Initial configuration with four prey species}
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Unpalatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
  																										& 50 & \multicolumn{2}{c|}{\multirow{4}{*}{10}} \\ \cline{2-4}
  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}
  					 																					& 50 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{1400} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{2500} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species}
\label{tab:config-table-4-prey}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10k-4Prey}
	\caption[Population distribution of mimicry rings (4 prey species)]{Population distribution of mimicry rings, initialized with 4 prey species.}
	\label{fig:plot-4-prey}
\end{figure}

@@

\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
  \multirow{4}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} & 150 & \multicolumn{2}{c|}{\multirow{4}{*}{20}} \\ \cline{2-4}
  					 									& Rule30 (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  	 & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}  & 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2500} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 4 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 4 prey species with increased population}
\label{tab:config-table-4-more-prey}
\end{table}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/simTime10K-4MorePrey}
	\caption[Population distribution of mimicry rings (4 prey species, increased population)]{Population distribution of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:plot-4-more-prey}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{../tex/images/ringSize10k-4MorePrey}
	\caption[Number of mimicry rings (4 prey species, increased population)]{Number of mimicry rings, initialized with 4 prey species with increased population.}
	\label{fig:ringSize10k-4MorePrey}
\end{figure}

\subsection{Initial population with six prey species}
\label{subsec:init-conf-6-prey}
\begin{table}[h]
\centering
\setlength\tabcolsep{2pt}
\begin{tabular}{| p{2cm} | p{1.5cm} | p{1cm} | p{.5cm} | p{1.5cm} | p{.5cm} |}
  \hline
   														&\multicolumn{3}{c|}{Prey configuration} 																	
   														& \multicolumn{2}{c|}{\parbox{2cm}{Predator configuration}} \\ \hline
  \multirow{6}{*}{Population} & Rule110 (Palatable) & \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule110}} 
  																									& 150 & \multicolumn{2}{c|}{\multirow{6}{*}{30}} \\ \cline{2-4}
  					 									& Rule30  (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule30}}  
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule55  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule55}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule190 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule190}} 
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule57  (Palatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule57}}    
  					 																				& 150 & \multicolumn{2}{c|}{}\\ \cline{2-4}
  					 									& Rule105 (Unpalatable)& \parbox[c]{2.1em}{\includegraphics[scale=0.50]{../tex/images/CARule105}}& 150 & \multicolumn{2}{c|}{}\\ \hline
  \multirow{2}{*}{Reproduction} & Age Limit & \multicolumn{2}{c|}{100}  & \multicolumn{2}{c|}{500} \\ \cline{2-6}
  						 									& Interval  & \multicolumn{2}{c|}{1000} & \multicolumn{2}{c|}{2000} \\ \hline
  \multirow{2}{*}{Mutation Rate} & Pattern   & \multicolumn{2}{c|}{0.05} & \multicolumn{2}{c|}{\multirow{2}{*}{0.3}} \\ \cline{2-4}
  						 									 & Genome    & \multicolumn{2}{c|}{0.5}  & \multicolumn{2}{c|}{} \\ \hline
  Demise Age	 									 & \multicolumn{3}{c|}{2000}							& \multicolumn{2}{c|}{7000} \\ \hline
  Minimum Attack Age						 & \multicolumn{3}{c|}{} 						    & \multicolumn{2}{c|}{500} \\ \hline
  \multirow{2}{*}{\parbox{2cm}{Memory Configuration}} & \multicolumn{3}{c|}{} 					& Minimum & 6 \\ \cline{5-6}
   																			& \multicolumn{3}{c|}{} 					& Maximum & 10 \\ \hline  
\end{tabular}
\caption{Agent configuration of 6 prey species.}
\label{tab:config-table-6-prey}
\end{table}
